### 2012-06-21 inst/examples/Reed.Rmd
critical transition examples
local edits on zero

``` {r  echo=FALSE }
opts_knit$set(upload.fun = socialR::flickr.url)
orig = getOptions("device")
options(device = function(width = 5, height = 5) {
    pdf(NULL, width = width, height = height)
})
knitcitations::cleanbib()
````

>>>>

``` {r  echo=FALSE, cache=FALSE}
opts_knit$set(upload.fun = socialR::flickr.url)
orig = getOption("device")
options(device = function(width = 5, height = 5) {
    pdf(NULL, width = width, height = height)
})
knitcitations::cleanbib()
````

### 2012-06-21 inst/examples/voi_sethi_parameters.Rmd
local edits on zero

``` {r runall}
det <- scenario(0.1, 0.0, 0.0)
g   <- scenario(0.5, 0.0, 0.0)
m   <- scenario(0.0, 0.5, 0.0)
i   <- scenario(0.0, 0.0, 0.5)
gm  <- scenario(0.5, 0.5, 0.0)
gi  <- scenario(0.5, 0.0, 0.5)
im  <- scenario(0.0, 0.5, 0.5)
gmi <- scenario(0.5, 0.5, 0.5)
````

@@

``` {r sethiplots, dependson="runall"}
require(reshape2)
policy <- melt(data.frame(stock = x_grid, det = det$D[,1], g = g$D[,1], m = m$D[,1], i= m$D[,i], gm = gm$D[,1], gi = gi$D[,1], gmi = gmi$D[,1]), id = "stock")
ggplot(policy) + 
  geom_point(aes(stock, stock-x_grid[value], color=variable)) +
	geom_smooth(aes(stock, stock-x_grid[value], color=variable)) +
  ylab("escapement")

@@

``` {r runallsims} 
policyfn <- list(det=det, g=g, m=m, i=i, gm=gm, gi=gi, gmi=gmi)
noise <- list(s0=c(0,0,0), sg=c(.2, 0, 0), sm=c(0, .2, 0), si=c(0,0,.2), sgm=c(.2, .2, 0), sgi=c(.2, 0, .2), sgmi=c(.2, .2, .2)) 
allcases <- lapply(policyfn, function(policyfn_i){
  lapply(noise, function(noise_i){
    simulatereps(policyfn_i, noise_i[1], noise_i[2], noise_i[3])
  })
})
````

>>>>

``` {r runall}
lvl <- 0.1
det <- scenario(0.01, 0.0, 0.0)
g   <- scenario(lvl, 0.0, 0.0)
m   <- scenario(0.0, lvl, 0.0)
i   <- scenario(0.0, 0.0, lvl)
gm  <- scenario(lvl, lvl, 0.0)
gi  <- scenario(lvl, 0.0, lvl)
im  <- scenario(0.0, lvl, lvl)
gmi <- scenario(lvl, lvl, lvl)
````

@@

``` {r sethiplots, dependson="runall"}
require(reshape2)
policy <- melt(data.frame(stock = x_grid, det = det$D[,1], 
               g = g$D[,1], m = m$D[,1], i= m$D[,i], 
               gm = gm$D[,1], gi = gi$D[,1], gmi = gmi$D[,1]), 
               id = "stock")

ggplot(policy) + 
  geom_point(aes(stock, stock-x_grid[value], color=variable)) +
	geom_smooth(aes(stock, stock-x_grid[value], color=variable)) +
  ylab("escapement")

@@

``` {r runallsims} 
policyfn <- list(det=det, g=g, m=m, i=i, gm=gm, gi=gi, gmi=gmi)
noise <- list(s0=c(0,0,0), sg=c(lvl, 0, 0), sm=c(0, lvl, 0), si=c(0,0,lvl), sgm=c(lvl, lvl, 0), sgi=c(lvl, 0, lvl), sgmi=c(lvl, lvl, lvl)) 
allcases <- lapply(policyfn, function(policyfn_i){
  lapply(noise, function(noise_i){
    simulatereps(policyfn_i, noise_i[1], noise_i[2], noise_i[3])
  })
})
````
